Forecasting the United States 2024 Presidential Election

### 2024-11-04 paper/paper.qmd
added survey monkey question randomization feature

A sample implementation of such poll, created using Google form, can be found [here](https://forms.gle/ti2rjGGVxBukv9dF6). In this version, the order of questions presented is consistent for all respondents due to the limitations of Google form, but for an idealized methodology with more professional surveying platform, the question order should be randomized when being presented to different respondents. This will help reduce response order bias, which is when the answer of a question is affected by the order in which it appeared in the survey [@citeStantcheva].

>>>>

A sample implementation of such poll, created using Google form, can be found [here](https://forms.gle/ti2rjGGVxBukv9dF6). In this version, the order of questions presented is consistent for all respondents due to the limitations of Google form, but for an idealized methodology with more professional surveying platform, such as Survey Monkey, the question order would be randomized when being presented to different respondents with the Question Randomization feature [@surveymonkey]. This will help reduce response order bias, which is when the answer of a question is affected by the order in which it appeared in the survey [@citeStantcheva].
